---
title: "Basic usage of the currency package"
author: "Michael Andrec"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic usage of the currency package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Generating a `currency` object


```{r echo=TRUE, message=FALSE, warning=FALSE}
require(currency)
```


```{r}
as.currency(20)

as.currency(200000000)

as.currency(200000000, type="JPY")
```

## Arithmetic operations

The `currency` class inherits from the base R `numeric` class, so all of the standard arithmetic operations work as expected. The result is either of class `currency` or `numeric`, depending on what makes sense based on [dimensional analysis](https://en.wikipedia.org/wiki/Dimensional_analysis): if the result has a meaningful currency unit under the assumption that any `numeric` participating in a binary arithmetic operation is dimensionless, then the result will be `currency`, otherwise it will be `numeric`. 

```{r}
twenty <- as.currency(20)
thirty <- as.currency(30)

twenty + thirty

twenty/0.001

10/twenty # numeric, would have units of "per dollar"

2*twenty

twenty*thirty # numeric, would have units of "dollar^2"

log10(thirty)

sqrt(twenty)

mean(c(twenty, thirty)) # what should this be?

```

## Original currency values

The `currency` object extends the `numeric` class with two additional slots that store the original, uncoverted currency value and the original currency type.

```{r}
yen <- as.currency(200, type="JPY")

yen

format(yen, original=TRUE)
```

For the results of an arithmetic operations that return `currency`, the original values are set appropriately if it makes sense to do so.

```{r}
format(twenty + thirty, original=TRUE) # OK

format(twenty + yen, original=TRUE) # NO

format(2*yen, original=TRUE) # OK

format(yen/0.001, original=TRUE) # OK
```
